The \project{unRAVE} catalog

### 2016-08-22 article/unrave.tex
Triggering dd
Trigger
muh triggers
Nothing
Comment to trigger dd
fuck
fix shit with dd
sick of this
grr
test
Include comparison figures (as PNGs, temporarily)
Fix citation to Kordopatis

\usepackage{amsmath,amssymb}
\usepackage{bm}

@@

\newcommand{\project}[1]{\textsl{#1}}
\newcommand{\thecannon}{\project{The~Cannon}}
\newcommand{\acronym}[1]{{\small{#1}}}
\newcommand{\rave}{\project{\acronym{RAVE}}}
\newcommand{\logg}{\log g}
\newcommand{\teff}{T_{\mathrm{eff}}}
\newcommand{\argmin}[1]{\underset{#1}{\operatorname{argmin}}\,}
\newcommand{\stub}[1]{\textbf{#1}}
\newcommand{\Nstars}{483,330}
\newcommand{\gaia}{\project{Gaia}}

@@

% Specific contributors to this work
\author{Some combination of: Harry Enke, Gerry Gilmore, Keith Hawkins, David W. Hogg, Georges Kordopatis, Gal Matijevic, Melissa Ness, Jason Sanders, Matthias Steinmetz, Hans Walter-Rix}

% RAVE DR5 core team
\author{Luca Casagrande, Cristina Chiappini, Andrea Kunder, Paul McMillan, Alessandro Siviero, Marica Valentini, Jennifer Wojno, Toma{\^z} Zwitter}

\author{and the \project{RAVE} collaboration}

%\altaffiltext{3}{\texttt{arc@ast.cam.ac.uk}}

\begin{abstract}

The Milky Way may be our greatest laboratory for understanding galaxy formation.
This premise relies on the ability to measure [1] 3D positions and motions, and
[2] detailed chemical abundances, for large numbers of individual stars.  On 14
September 2016 the \gaia\ mission will release the former for $\approx2\times10^6$
stars.  However, a catalog of precise chemical abundances to complement that data
release is currently lacking.  The RAdial Velocity Experiment (\rave) survey has 
acquired spectra for 292,036 stars in common with the first \gaia\ data release, 
constituting the largest overlap of any stellar spectroscopic sample.  Here we 
perform an independent analysis of \rave\ spectra using an implementation of 
\thecannon\ that uses prior probabilities on atomic line formation and stellar
astrophysical parameters.  Our approach yields precise stellar labels at lower
S/N ratios than most \emph{ab initio} approaches, allowing us to deliver
improved radial velocities, effective temperature $\teff$, surface gravity $\logg$,
and chemical abundances of up to seven elements (Mg, Al, Si, Ca, Ti, Fe, Ni) 
for \Nstars\ stars.  We validate our results internally from repeat visits, 
and externally against existing high-resolution spectroscopic surveys.  The 
typical precision in chemical abundances is X.XX~dex.  We provide 
spectrophotometric distances based on our labels, improving upon the parallax
distances available for the fainter targets in the first \gaia\ data release.
% A one-line science result based on RAVE/Hipparcos overlap.
\end{abstract}

@@

\begin{figure*}[p]
\caption{Stellar label comparison between the \project{UNRAVE} catalog and the \project{RAVE} fourth data release \citep{Kordopatis_2014}.\label{fig:rave-dr4-comparison}}
\end{figure*}

@@

\begin{figure*}[p]
\caption{Stellar label comparison between the \project{UNRAVE} catalog and the \project{Gaia-ESO Survey} fourth internal data release.\label{fig:ges-dr4-comparison}}
\end{figure*}

\begin{figure*}[p]
\caption{Stellar label comparisons between the \project{UNRAVE} catalog and the samples discussed in \citep{Kordopatis_2014}}
\end{figure*}

>>>>

\usepackage{amsmath}
\usepackage{bm}

@@

\newcommand{\project}[1]{\textsl{#1}}
\newcommand{\gaia}{\project{Gaia}}
\newcommand{\thecannon}{\project{The~Cannon}}
\newcommand{\rave}{\project{\acronym{RAVE}}}

\newcommand{\acronym}[1]{{\small{#1}}}

\newcommand{\stub}[1]{\textbf{#1}}

\newcommand{\teff}{T_{\mathrm{eff}}}
\newcommand{\logg}{\log g}

\newcommand{\Nstars}{483,330}

\newcommand{\argmin}[1]{\underset{#1}{\operatorname{argmin}}\,}

@@

% Specific contributors to this work:
% There is some order already in mind, but final order will be determined by  contribution.
\author{Some combination of: Harry Enke, Gerry Gilmore, Keith Hawkins, David W. Hogg, Georges Kordopatis, Gal Matijevic, Melissa Ness, Jason Sanders, Matthias Steinmetz, Hans Walter-Rix}

% RAVE DR5 core team:
\author{Luca Casagrande, Cristina Chiappini, Andrea Kunder, Paul McMillan, Alessandro Siviero, Marica Valentini, Jennifer Wojno, Toma{\^z} Zwitter}

\author{and the \rave\ collaboration}

\begin{abstract}
The Milky Way may be our greatest laboratory for understanding galaxy formation.
This premise relies on the ability to measure [1] 3D positions and motions, and
[2] detailed chemical abundances, for large numbers of individual stars.  On 14
September 2016 the \gaia\ mission will release the former for $\approx2\times10^6$
stars.  However, a catalog of precise chemical abundances to complement that data
release is currently lacking.  The RAdial Velocity Experiment (\rave) survey has 
acquired spectra for 292,036 stars in common with the first \gaia\ data release, 
constituting the largest overlap of any stellar spectroscopic sample.  Here we 
perform an independent analysis of \rave\ spectra using an implementation of 
\thecannon\ that uses prior probabilities on atomic line formation and stellar
astrophysical parameters.  Our approach yields precise stellar labels at lower
S/N ratios than most \emph{ab initio} approaches, allowing us to deliver
improved radial velocities, effective temperature $\teff$, surface gravity $\logg$,
and chemical abundances of up to seven elements (Mg, Al, Si, Ca, Ti, Fe, Ni) 
for \Nstars\ stars.  We validate our results internally from repeat visits, 
and externally against existing high-resolution spectroscopic surveys.  The 
typical precision in chemical abundances is X.XX~dex.  We provide 
spectrophotometric distances based on our labels, improving upon the parallax
distances available for the fainter targets in the first \gaia\ data release.
\stub{A one-line science result based on RAVE/Hipparcos overlap}
\end{abstract}

@@

\begin{figure*}[p]
\includegraphics[width=\textwidth]{figures/dr4-comparison.png}
\caption{Stellar label comparison between the \project{UNRAVE} catalog and the \project{RAVE} fourth data release \citep{Kordopatis_2013}.\label{fig:rave-dr4-comparison}}
\end{figure*}

@@

\begin{figure*}[p]
\includegraphics[width=\textwidth]{figures/ges-comparison.png}
\caption{Stellar label comparison between the \project{UNRAVE} catalog and the \project{Gaia-ESO Survey} fourth internal data release.\label{fig:ges-dr4-comparison}}
\end{figure*}

\begin{figure*}[p]
\includegraphics[width=\textwidth]{figures/literature-comparison.png}
\caption{Stellar label comparisons between the \project{UNRAVE} catalog and the samples discussed in \citep{Kordopatis_2013}}
\end{figure*}
